Biogears in Anesthesia Screen Based Simulation

### 2016-02-27 paper_working_on/paper.tex
add cae data, modify pictures for biogears simulation and add one paper

\graphicspath{{cae_simulation_result/}}
\title{Biogears in Anesthesia Screen Based Simulation}

\author{
  Xiao Han\\
  \and Liewei Ke
  \and Guan Wang
  \and Mclvor William
}

@@

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/bleeding_out_HeartRate_vs_Time.jpg}}
     \caption{heart rate changes}
     \label{fig:patient bleeding}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/bleeding_out_RespirationRate_vs_Time.jpg}}
     \caption{respiratory rate changes}
     \label{fig:patient bleeding}
   \end{minipage}
\end{figure}

@@

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/30_OxygenSaturation_vs_Time.jpg}}
     \caption{oxygen saturation changes}
     \label{fig:patient stoping breathing}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/120_OxygenSaturation_vs_Time.jpg}}
     \caption{oxygen saturation changes}
     \label{fig:patient stoping breathing}
   \end{minipage}
\end{figure}

@@

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Succinylcholine_HeartRate_vs_Time.jpg}}
     \caption{Heart Rate changes}
     \label{fig:given 5 mg Succinylcholine}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Succinylcholine_OxygenSaturation_vs_Time.jpg}}
     \caption{Oxygen Saturation changes}
     \label{fig:given 5 mg Succinylcholine}
   \end{minipage}
\end{figure}

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Succinylcholine_ArterialPressure_vs_Time.jpg}}
     \caption{Blood Pressure changes}
     \label{fig:given 5 mg Succinylcholine}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Succinylcholine_RespirationRate_vs_Time.jpg}}
     \caption{Respiration Rate changes}
     \label{fig:given 5 mg Succinylcholine}
   \end{minipage}
\end{figure}

@@

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Rocuronium_HeartRate_vs_Time.jpg}}
     \caption{Heart Rate changes}
     \label{fig:given 50 mg Rocuronium}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Rocuronium_OxygenSaturation_vs_Time.jpg}}
     \caption{Oxygen Saturation changes}
     \label{fig:given 50 mg Rocuronium}
   \end{minipage}
\end{figure}

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Rocuronium_ArterialPressure_vs_Time.jpg}}
     \caption{Blood Pressure changes}
     \label{fig:given 50 mg Rocuronium}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Rocuronium_RespirationRate_vs_Time.jpg}}
     \caption{Respiration Rate changes}
     \label{fig:given 50 mg Rocuronium}
   \end{minipage}
\end{figure}

@@

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Propofol_HeartRate_vs_Time.jpg}}
     \caption{Heart Rate changes}
     \label{fig:given 200 mg Propofol}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Propofol_OxygenSaturation_vs_Time.jpg}}
     \caption{Oxygen Saturation changes}
     \label{fig:given 200 mg Propofol}
   \end{minipage}
\end{figure}

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Propofol_ArterialPressure_vs_Time.jpg}}
     \caption{Blood Pressure changes}
     \label{fig:given 200 mg Propofol}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Propofol_RespirationRate_vs_Time.jpg}}
     \caption{Respiration Rate changes}
     \label{fig:given 200 mg Propofol}
   \end{minipage}
\end{figure}

@@

@@

>>>>

\graphicspath{{cae_simulation_result/}{biogears_simulation_result/}}

%\graphicspath{{biogears_simulation_result/30_and_120_stop_breathing}}
%\graphicspath{{biogears_simulation_result/bleeding_out}}
%\graphicspath{{biogears_simulation_result/Propofol200mg}}
%\graphicspath{{biogears_simulation_result/Fentanyl500ug}}
%\graphicspath{{biogears_simulation_result/Rocuronium50mg}}
%\graphicspath{{biogears_simulation_result/Morphine40mg}}
%\graphicspath{{biogears_simulation_result/Succinylcholine5mg}}

\title{Biogears in Anesthesia Screen Based Simulation}

\author{
  Xiao Han\\
  \and Guan Wang\\
  \and Liewei Ke\\
  \and Mclvor William
}

@@

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{bleeding_out/bleeding_out_HeartRate_vs_Time.jpg}}
     \caption{heart rate changes}
     \label{fig:patient bleeding}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{bleeding_out/bleeding_out_RespirationRate_vs_Time.jpg}}
     \caption{respiratory rate changes}
     \label{fig:patient bleeding}
   \end{minipage}
\end{figure}

@@

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{30_and_120_stop_breathing/30_OxygenSaturation_vs_Time.jpg}}
     \caption{oxygen saturation changes}
     \label{fig:patient stoping breathing}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{30_and_120_stop_breathing/120_OxygenSaturation_vs_Time.jpg}}
     \caption{oxygen saturation changes}
     \label{fig:patient stoping breathing}
   \end{minipage}
\end{figure}

@@

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{Succinylcholine5mg/Succinylcholine_ArterialPressure_vs_Time.jpg}}
     \caption{Blood Pressure changes}
     \label{fig:given 5 mg Succinylcholine}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{Succinylcholine5mg/Succinylcholine_RespirationRate_vs_Time.jpg}}
     \caption{Respiration Rate changes}
     \label{fig:given 5 mg Succinylcholine}
   \end{minipage}
\end{figure}

The problem with those results are that:1. Simulation result of Arterial Pressure

@@

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{Rocuronium50mg/Rocuronium_HeartRate_vs_Time.jpg}}
     \caption{Rocu Heart Rate changes }
     \label{fig:given 50 mg Rocuronium}

   \end{minipage}
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{Rocuronium50mg/Rocuronium_ArterialPressure_vs_Time.jpg}}
     \caption{Rocu Blood Pressure changes}
     \label{fig:given 50 mg Rocuronium}

   \end{minipage}
\end{figure}

The respiratory rate and oxygen saturation both looks fine when this drug took effect. But Rocuronium was not supposed to cause patient's Arterial Pressure to go up, stay for a minute and then plummet to the bottom. Instead, we should see its signal functuating around normal level. Also, heart rate graph was supposed to look flat and then fell off cause patient's heart is dying with the drug.

@@

\begin{figure}[!htb]\centering

\end{figure}

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{Propofol200mg/Propofol_HeartRate_vs_Time.jpg}}
     \caption{Heart Rate changes}
     \label{fig:given 200 mg Propofol}
     \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{Propofol200mg/Propofol_RespirationRate_vs_Time.jpg}}
     \caption{Respiration Rate changes}
     \label{fig:given 200 mg Propofol}
   \end{minipage}
\end{figure}

Propofol has a fine-looking simulation of Arterial Pressure, but there appeared to be problems with its heart rate and respiratory rate simulation. In the heart rate graph at around 30 - 40 seconds, the pumping rate was not supposed to go down as well as rise again. In the respiratory rate graph its reading went down and indicated patient stopped breathing after certain point. But we expected the patient to start breathing again and recover at some point because we gave normal dosage for Propofol to function as anaesthetic.

We then ran the same experiment using Muse and visualize the data, the simulation lasts for 
10 minutes:

@@

Morphine is probably the most common drug that's been used to reduce patients' pain. However, it is worth paying attention to if large dosage of morphine is injected into patients because that could cause difficulty breathing, nausea and even death of patients. So in medical simulation, it is important to simulate its effect accurately for training.

In our experiment, we set up the dosage to be 40 mg for Biogears and ran it for 9 minutes. The results are as followed:

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{Morphine40mg/Morphine_HeartRate_vs_Time.jpg}}
     \caption{Heart Rate changes}
     \label{fig:given 40 mg Morphine}
   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{Morphine40mg/Morphine_RespirationRate_vs_Time.jpg}}
     \caption{Respiration Rate changes}
     \label{fig:given 40 mg Morphine}
   \end{minipage}
\end{figure}

In reality, Injecting a normal person with 40mg morphine is enough to cause him/her heartrate dropping, less breathing which leads to death eventually. However, it seems dramatically increasing morphine dosage won't  
be able to cause patient death which will be a problem if it was utilized for medical training.

@@

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{Fentanyl500ug/Fentany_HeartRate_vs_Time.jpg}}
     \caption{Heart Rate changes}
     \label{fig:given 500 ug Fentanyl}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{Fentanyl500ug/Fentany_OxygenSaturation_vs_Time.jpg}}
     \caption{Oxygen Saturation changes}
     \label{fig:given 500 ug Fentanyl}
   \end{minipage}
\end{figure}

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{Fentanyl500ug/Fentany_ArterialPressure_vs_Time.jpg}}
     \caption{Blood Pressure changes}
     \label{fig:given 500 ug Fentanyl}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{Fentanyl500ug/Fentany_RespirationRate_vs_Time.jpg}}
     \caption{Respiration Rate changes}
     \label{fig:given 500 ug Fentanyl}
   \end{minipage}
\end{figure}
